Strong coupling between scales in a multi-scalar model of urban dynamics

### 2022-11-03 Docs/Papers/Multiscale/paper/paper.tex
.

Future work also implies the use of more elaborated model exploration and validation methods. For example, using the diversity search integrated in OpenMOLE \cite{reuillon2013openmole} would allow unveiling the diversity of possible future urban trajectories, and possibly unexpected novel pathways towards sustainability, finding for example regimes with the strongest effect of feedback parameters on indicators related to sustainability.
% spatial sensitivity - influence of synthetic system of cities

>>>>

Future work also implies the use of more elaborated model exploration and validation methods. For example, using the diversity search integrated in OpenMOLE \citep{reuillon2013openmole} would allow unveiling the diversity of possible future urban trajectories, and possibly unexpected novel pathways towards sustainability, finding for example regimes with the strongest effect of feedback parameters on indicators related to sustainability.
% spatial sensitivity - influence of synthetic system of cities
